On the adhesivity of EGGS

### 2025-02-20 calco/main.tex
minima
minori

From the previous result we can now deduce that the class of regular epis is closed under colimits, as shown by the next lemma
\begin{restatable}{lemma}{epicol}\label{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
    Let $F,G'\colon \D\rightrightarrows \X$ be two diagrams, and suppose that $\X$ has all colimits of shape $\D$. Let $(X, \{x_d\}_{d \in \D})$ and $(Y, \{y_d\}_{d\in \S})$ be, respectively, the colimit of $F$ and $G$.  If $\phi\colon  F \to G$ is a natural transformation in which all components are regular epimorphisms, then, the arrow induced by $\phi$ from $X$ to $Y$ is a regular epimorphism too.
\end{restatable}
[Proof in \Cref{epicol-proof}]

>>>>

From the previous result we can now deduce that the class of regular epis is closed under colimits, as shown by the next lemma
\begin{restatable}{lemma}{epicol}\label{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
    Let $F,G\colon \D\rightrightarrows \X$ be two diagrams, and suppose that $\X$ has all colimits of shape $\D$. Let $(X, \{x_d\}_{d \in \D})$ and $(Y, \{y_d\}_{d\in \S})$ be, respectively, the colimit of $F$ and $G$.  If $\phi\colon  F \to G$ is a natural transformation in which all components are regular epimorphisms, then, the arrow induced by $\phi$ from $X$ to $Y$ is a regular epimorphism too.
\end{restatable}
[Proof in \Cref{epicol-proof}]
